---
title: "Unit 4 - 6 Review Starter"
author: "Gavin"
date: "Nov 1, 2021"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(lubridate)
library(janitor)
```

## Exercises

# Part I - Data Types and Classes

## Exercise 1 - Create some vectors

```{r month-name-vector}
month_name <- c("January", 
                "February",
                "March",
                "April",
                "May",
                "June",
                "July",
                "August",
                "September",
                "October",
                "November",
                "December")
```

#### Member 1

```{r}

tunes <- c("bloons", "moons", "vrooms", "grooms", "rooms", "wooms", "pooms", "zooms", "looms", "quooms", "noons", "booms")

tunes
```


#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 2 - Combine into a data frame

```{r merge-two-vectors, eval = F}
month_tunes <- tibble::tibble(
  "month_name" = month_name,
  "tunes" = tunes
)

glimpse(month_tunes)
```

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 3 - Try plotting with `month_name` on the x axis, then recode factors


```{r}
nuumbers <- c(1, 2, 3, 4, 5, 5, 6, 6, 4, 3, 9, 10)


month_tuunes <- tibble::tibble(
  "month_name" = month_name,
  "tunes" = tunes, 
  "nuumbers" = nuumbers
)
```



```{r}
 
month_tuuunes <- month_tuunes %>% 
  mutate(month_name = fct_relevel(month_name, "January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December"))
    
month_tuuunes %>% 
  ggplot(aes(month_name, nuumbers)) +
  geom_point()

```


#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 4 - Join all the data frames, filter randomly, and over-write vector

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 5 - Try to recombine as a data frame, instead use list

```{r try-merge-vectors, eval = F}
___ <- tibble::tibble(
  "month_name" = month_name,
  "___" = ___
)
```

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.
